\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{enumitem}

\hypersetup{%
	colorlinks=true,
	linkcolor=blue,
	linkbordercolor={0 0 1}
}
 
\renewcommand\lstlistingname{Algorithm}
\renewcommand\lstlistlistingname{Algorithms} 
\def\lstlistingautorefname{Alg.}

\lstdefinestyle{Python}{
		language        = Python,
		frame           = lines, 
		basicstyle      = \footnotesize,
		keywordstyle    = \color{blue},
		stringstyle     = \color{green},
		commentstyle    = \color{red}\ttfamily
}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

% Edit these as appropriate
\newcommand\course{MATH 225}
\newcommand\hwnumber{1.2}
\newcommand\HWnum{Homework 2}
\newcommand\SName{Luke Mattfeld}          

\pagestyle{fancyplain}
\headheight 35pt
\lhead{\HWnum}
\lhead{\HWnum\\\SName}                 % <-- Comment this line out for problem sets (make sure you are person #1)
\chead{\textbf{\Large Section \hwnumber}}
\rhead{\course \\ April 5, 2019}
\lfoot{}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em

\begin{document}


\section*{1.}
\begin{enumerate}
	\item[\textbf{b)}]
		Antecedent: ``The moon is made of cheese"\\
		Consequent: ``8 is an irrational number"
	\item[\textbf{c)}]
		Antecedent: ``\textit{b} divides 3"\\
		Consequent: ``\textit{b} divides 9"
	\item[\textbf{e)}]
		Antecedent: ``\textit{a} is convergent"\\
		Consequent: ``A sequence \textit{a} is bounded"
	\item[\textbf{g)}]
		Antecedent: ``$1+1=2$"\\
		Consequent: ``$1+2=3$" 
	\item[\textbf{h)}]
		Antecedent: ``The fish bite"\\
		Consequent: ``The moon is full" 
\end{enumerate}


\section*{2.}
\begin{enumerate}
	\item[\textbf{b)}]
		Converse: ``If 8 is an irrational number, then the moon is made of cheese"\\
		Contrapositive: ``If 8 is not an irrational number, then the moon is not made of cheese" 
	\item[\textbf{c)}]
		Converse: ``\textit{b} divides 9 only if \textit{b} divides 3"\\
		Contrapositive: ``\textit{b} does not divide 9 only if \textit{b} does not divide 3"  
	\item[\textbf{e)}]
		Converse: ``A sequence \textit{a} is convergent whenever \textit{a} is bounded"\\
		Contrapositive: ``A sequence \textit{a} is not convergent whenever \textit{a} is unbounded"  
	\item[\textbf{g)}]
		Converse: ``$1+1=2$ is necessary for $1+2=3$"\\
		Contrapositive: ``$1+1\neq2$ is necessary for $1+2\neq3$"  
	\item[\textbf{h)}]
		Converse: ``The moon is full only when the fish bite"\\
		Contrapositive: ``The moon is not full only when the fish don't bite"  
\end{enumerate}

\newpage
\section*{5.}
\begin{enumerate}
	\item[\textbf{b)}]
		``Hexagons have size sides'' $\rightarrow$ true\\
		``The moon is made of cheese'' $\rightarrow$ false\\
		$T \rightarrow F \equiv F$, so this statement is false.
	\item[\textbf{d)}]
		``The Nile River flows east'' $\rightarrow$ false\\
		``64 is a perfect square'' $\rightarrow$ true\\
		$F \rightarrow T \equiv T$, so this statement is true. 
	\item[\textbf{e)}]
		``Earth has one moon'' $\rightarrow$ true\\
		``The Amazon River flows into the North Sea'' $\rightarrow$ false\\
		$T \rightarrow F \equiv F$, so this statement is false.  
	\item[\textbf{f)}]
		``Euclid's birthday was April 2'' $\rightarrow$ ?\\
		``Rectangles have four sides'' $\rightarrow$ true\\
		The antecedent is true, so this statement is true. 
	\item[\textbf{g)}]
		``$\sqrt{2}$ is not irrational'' $\rightarrow$ false\\
		``5 is prime'' $\rightarrow$ true\\
		$F \rightarrow T \equiv T$, so this statement is true. 
	\item[\textbf{h)}]
		``$1+1=2$'' $\rightarrow$ true\\
		``$3 > 6$'' $\rightarrow$ false\\
		$T \rightarrow F \equiv F$, so this statement is false. 
\end{enumerate}


\section*{14.}
\begin{enumerate}[label= \textbf{\alph*)}]
	\item "If 3 is an integer, then this class does not have a textbook."
	\item This is not possible, since if a conditional is false it's converse
		will always be true. This is because all other combinations of truth values
		for P and Q in a conditional statement lead to a true statement.
	\item "If earth is a planet, then this sentence does not exist."
	\item This is not possible, since the contrapositive of a conditional always
		has the same truth value of the original conditional statement. Thus a
		false conditional can never have a true contrapositive.
\end{enumerate}

\end{document}